The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190925.tex
CIV tex/ tidy up

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  However, dramatic
changes in the broad emission lines (BELs) in quasars has only
recently been identified \citep[e.g.][]{LaMassa2015}.  Samples of over
100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars
(CSQs) have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}.
The community uses both these terms as a cover for the underlying
physics. For sake of argument, ``Changing Look'' quasars can
potentially be thought of as the extension to the BELs of quasar
continuum variability \citep[e.g.][]{MacLeod2012} whereas the
``Changing State'' quasars (CSQs) have a `state-transition' similar to
that in Galactic X-ray binaries \citep[e.g][]{NodaDone2018,
Ruan2019}. In this paper, we use the term `Changing Look', as we are
currently agnostic, and somewhat ignorant, to the underlying physical
processes.

@@

While there have been a slew of studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019} or the Baldwin Effect
\citep[BEff; e.g. ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an
anti-correlation between the EW of the emission line and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line (BEL) of \civ (and
indeed \ciii) have not to this point been seen.

Here, we report on three quasars  
%SDSS J120544.7+342252.4  (hereafter J1205+3422), 
%SDSS J163852.93+282707.7 (hereafter J1638+2827) and
%SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in their \civ\ and \ciii broad emission
line properties as well as in the underlying continuum. We claim these
are the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are the first cases for substantial changes
of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
linking the ionizing photons to the energetic inner accretion disk,
potentially by inverse Compton scattering lower energy photons to
higher energies.  Furthermore, the measured rest-wavelengths of
emission lines in quasar spectra, are known to vary from their nominal
laboratory especially for the high-ionization broad lines,
wavelengths, \citep[e.g.][]{VandenBerk2001}.

In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for
the \civ doublet \citep{Kramida2018}. The ground state of carbon is
1$s^2$ 2$s^2$ 2$p^2$.  Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we see 11.3 eV is the energy needed for C I to dislodge one
electron and become singly-ionised C II; 24.4 eV is energy needed for
singly-ionised C II to dislodge an additional electron, and become
doubly-ionised C III, and 47.89 eV (3.519 Ry) is required for
doubly-ionised C III become triply--ionised \civ.  64.49 eV (4.74 Ry)
is the energy needed to ionize \civ itself. The 1548.202 and 1550.774
\AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$
$^{2}S$ transition with energies 64,484 cm$^{-1}$ and 64,591 cm$^{-1}$
\citep[e.g.][]{Moore1993}.

%%       B a c k g r o u n d     L i t e r a t u r e    
\civ\ variability has been long studied, \citep[e.g., ][]{Baldwin1977,
Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
Laor1995, McIntosh1999, Nazarova2003}.
%%
\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
of 105 quasars observed at multiple epochs by the SDSS.  They find a
strong correlation between the change in the C~\textsc{iv} line flux
and the change in the line width, but no correlations between the
change in flux and changes in line center and skewness.  These authors
find that the relation between line flux change and line width change
is consistent with a model in which a broad line base varies with
greater amplitude than the line core. The C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  \citet{Wilhite2006}
find no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.

\citet{Richards2011} explored the BELR in over 30,000 $z > 1.54$ SDSS
quasars, concentrating on the properties of the \civ\ emission
line. We consider two well-known effects involving the \civ\ emission
line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
the BEff) and the blueshifting of the peak of \civ\ emission with
respect to the systemic redshift. These authors conclude that these
two \civ\ parameters (EQW and blueshift) are capturing an important
trade-off between ``disk'' and ``wind'' components in the disk-wind
model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
Proga2000}.  with one dominating over the other depending on the shape
of the SED \citep[][strong \civ EQW indicates a more ionizing SED and
large \civ blueshift indicating a less ionizing SED]{Leighly2004b}.

@@

\civ has long been known to exhibit significant displacements to the
blue and these `blueshifts' almost certainly signal the presence of
strong outflows. As a consequence, single-epoch virial black hole (BH)
mass estimates derived from \civ velocity widths are known to be
systematically biased compared to masses from the hydrogen Balmer
lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
(LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with
both \civ and Balmer line spectra, we have quantified the bias in \civ
BH masses as a function of the \civ blueshift. \civ BH masses are
shown to be a factor of 5 larger than the corresponding Balmer-line
masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated
by almost an order of magnitude at the most extreme blueshifts,
$\gtrsim$5000 km s$^{-1}$.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
%%
Recent investigations also include \citet{Meyer2019}.

The purpose of this paper is, for the first time, to access and 
report on the ``Changing-Look'' quasar phenomenon at high, 
$z>2$ redshift. By doing so, we move from the low-ionization 
energy Balmer emission line series to the high-ionization emission 
lines, in particular \civ.

@@

@@

>>>>

The optical continuum variability of quasars has been recognized since
their first optical identification
\citep[e.g.,][]{MatthewsSandage1963, MacLeod2012}.  Dramatic
changes in the broad emission lines (BELs) of quasars has only
recently been identified \citep[e.g., ][]{LaMassa2015}.  Samples of over
100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars
(CSQs) have now been assembled \citep[e.g.][]{MacLeod2019,Graham2019}.
The community uses both these terms as a cover for the underlying
physics. For sake of argument, ``Changing Look'' quasars can
potentially be thought of as the extension to the BELs of quasar
continuum variability \citep[e.g., ][]{MacLeod2012} whereas the
``Changing State'' quasars (CSQs) have a `state-transition' similar to
that in Galactic X-ray binaries \citep[][]{NodaDone2018,
Ruan2019}. In this paper, we use the term `Changing Look', as we are
currently agnostic, and somewhat ignorant, to the underlying physical
processes.

@@

While there have been a slew of studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL QSOs; see Table 1][]{Hemler2019} or the Baldwin Effect
\citep[BEff; ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an
anti-correlation between the EW of the emission line and the
underlying continuum luminosity of {\it single-epoch} observations of
a {\it large number} of AGN and second, the {\it intrinsic} Baldwin
effect, the same anti-correlation but in an {\it individual, variable}
AGN \citep{PoggePeterson1992}.}.  Dramatic changes in the
collisionally excited broad {\it emission} line (BEL) of \civ\ (and
indeed \ciii) have not to this point been seen.

Here, we report on three quasars  
which show dramatic changes in their \civ\ and \ciii broad emission
line properties as well as in the underlying continuum. We claim these
are the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are the first cases for substantial changes
of ions with high ionization potentials (I.P.'s $>$2 Rydberg), thus
linking the ionizing photons to the energetic inner accretion disk,
potentially by inverse Compton scattering of lower energy photons to
higher energies.  Furthermore, the measured rest-wavelengths of
emission lines in quasar spectra, are known to vary from their nominal
laboratory wavelengths especially for the high-ionization broad lines \citep[e.g.][]{VandenBerk2001}.

In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}. The ground state of carbon is
1$s^2$ 2$s^2$ 2$p^2$.  Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we note 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply--ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. The 1548.202 and 1550.774 \AA\ emission doublet is created by
the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition with energies 64,484
cm$^{-1}$ and 64,591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.

%%       B a c k g r o u n d     L i t e r a t u r e    
\civ\ variability has been long studied, e.g., \citet[][]{Baldwin1977,
Gaskell1982, Gregory1982, Wilkes1986, Espey1989, Espey1990Erratum,
ZhengSulentic1990, Corbin1990, Corbin1991, Weymann1991,
Dimitrijevic1992, TytlerFan1992, Wills1993, Brotherton1994, Osmer1994,
Laor1995, McIntosh1999, Nazarova2003}.

\citet{Wilhite2006} examine
the variability of a C~\textsc{iv} sample of 105 quasars observed at
multiple epochs by the SDSS.  They find a strong correlation between
the change in the C~\textsc{iv} line flux and the change in the line
width, but no correlations between the change in flux and changes in
line center and skewness.  These authors find that the relation
between line flux change and line width change is consistent with a
model in which a broad line base varies with greater amplitude than
the line core. The C~\textsc{iv} lines in these high-luminosity
quasars appear to be less responsive to continuum variations than
those in lower luminosity AGN.  \citet{Wilhite2006} find no evidence
for variability of the well known blueshift of the C~\textsc{iv} line
with respect to the low-ionization Mg~\textsc{ii}$\lambda$2798 line in
the highest flux objects.

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
quasars, concentrating on the properties of the \civ\ emission
line. We consider two well-known effects involving the \civ\ emission
line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
the BEff) and the blueshifting of the peak of \civ\ emission with
respect to the systemic redshift. These authors conclude that these
two \civ\ parameters (EQW and blueshift) are capturing an important
trade-off between ``disk'' and ``wind'' components in the disk-wind
model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
Proga2000}.  with one dominating over the other depending on the shape
of the SED \citep[][strong \civ EQW indicates a more ionizing SED and
large \civ blueshift indicating a less ionizing SED]{Leighly2004b}.

@@

\civ is also known to exhibit significant displacements to the
blue and these `blueshifts' almost certainly signal the presence of
strong outflows. As a consequence, single-epoch virial black hole (BH)
mass estimates derived from \civ velocity widths are known to be
systematically biased compared to masses from the hydrogen Balmer
lines. \citet{Coatman2017} use a large sample of 230 high-luminosity
(LBol = 1045.5-1048 erg s-1), redshift $1.5 < z < 4.0$ quasars with
both \civ and Balmer line spectra, we have quantified the bias in \civ
BH masses as a function of the \civ blueshift. \civ BH masses are
shown to be a factor of 5 larger than the corresponding Balmer-line
masses at C IV blueshifts of 3000 km s$^{-1}1$ and are overestimated
by almost an order of magnitude at the most extreme blueshifts,
$\gtrsim$5000 km s$^{-1}$.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
%%
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}.

The purpose of this paper is, for the first time, to access and 
report on the Changing-Look quasar phenomenon at high, 
$z>2$ redshift. By doing so, we move from the low-ionization 
energy Balmer emission line series to the high-ionization emission 
lines, in particular \civ\ $lambda$1549.

@@

SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201). 
Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

@@

{\bf Our Eddington ratios \\
Done 1\% \\
Coatman, Hewett say \civ masses are okay.\\
But what are these Eddington ratios? \\
Low state BHs vs. High-mass BHs... \\
Coatman et al?? Blue-shiftted \\
}

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191001_MJG.tex
CIV tex/ tidy up

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first `Changing-Look'' quasars at high
redshift.  This is also the first time the changing-look behaviour has
been seen in a high-ionization emissions line.
%%
SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.
%%
Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
%%
Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z>2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
%%
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim10\%$ in Eddington luminosity.
\end{abstract}

@@

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ\ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ\ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ\ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ\ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
%%
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}.

@@

{\bf MJG to write a few notes on how the CIV CLQs were identified} 
lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
porta sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

@@

Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

@@

Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
nulla. Nullam eu augue id purus mollis dignissim sed et
libero. Phasellus eget justo sed neque pellentesque egestas nec id
arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
neque id mi ultrices tristique. Integer quam libero, ornare vel
gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
cursus, dui nisl egestas augue, non fermentum nisl est nec
nisi. Vestibulum nec mi justo, eget dapibus velit.

>>>>

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first `Changing-Look'' quasars at high
redshift.  This is also the first time the changing-look behaviour has
been seen in a high-ionization emission line.
%%
SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.
%%
Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
%%
Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z>2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
%%
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim10\%$ in Eddington luminosity.
\end{abstract}

@@

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ\ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ\ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ\ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ\ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
%%
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
results to.

@@

%{\bf MJG to write a few notes on how the CIV CLQs were identified} 
Our high-$z$ CLQs were identified as follows. 
We selected all 64,774 SDSS DR15 sources with $z > 0.35$ classified as
'QSO', having at least two spectra separated by at least 100 days, and
with a corresponding CRTS light curve. We fitted a damped random walk
to the CRTS data via Gaussian process regression and the photometric
magnitudes at the epochs of the SDSS spectra for a given source are
predicted. Those where $|\Delta V| > 0.3$ are then selected for visual
inspection.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwinn_20191003.png}
   \vspace{-12pt}
  \caption[]{The Baldwin Plot.}
  \label{fig:REWvsFWHM}
\end{figure}

\civ\ probes the photoionization environment produced by the innermost
disk, as indicated by RM time-delay measurements. In standard \citet{SS73}
thin disk models, large changes in the continuum flux are not
permitted over short timescales due to the relatively long viscous
time associated with such disks. Given the observed short timescale
continuum variations, it is not surprising that the \citet{SS73} disk may fail
on other fronts. The \civ\ variations observed in our sources... 
%DO/DO NOT (I can't tell!?! we have to determine this!) fit the Baldwin Effect relationship found by previous authors (cite em again).

%If they DO fit:
This indicates they may comfortably fit into the sample of CIV
variable QSOs explored by \citet{Dyer2019}, and similar to those
authors we suggest slim accretion disk models e.g., 
\citet[][]{Abramowicz1988} or inhomogeneous disk models
\citep[e.g.,][]{DexterAgol2011} may provide viable explanations for
our observations. I want to say a bit more here about the generic
probe of photoionization vs shielding and conditions in the BL region
but that will take more time.

%If they DO NOT fit:
This implies that the variable \civ\ in our sample arises through
different emission mechanisms than is usual for high-$z$ quasar...
%% --and I gotta think more/longer about what else to say here.
